Datasheet for 'A dataset

### 2024-03-10 paper/datasheet_template.qmd
update change

---
title: "Datasheet for 'A dataset'"
author: 
  - Yang Zhou
  - Yuean Wang
thanks: "Code and data are available at: LINK."
date: "`r Sys.time()`"
date-format: "09 March 2024"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The Cooperative Election Study (CES) aims to study how Americans perceive and hold their representatives accountable during elections. Besides, the study also interested in understanding their voting behavior and how their behavior be affected by political geography and social context. They study the group by capturing mass data across most of legislative constituencies. CES aims to fill the gap of understanding the American electoral process by analyzing congressional elections and national surveys.

@@

	- he CES 2022 dataset consists primarily of structured survey data collected from respondents about their political views, behaviors, and demographic information. Such data is generally not subject to legal privileges such as doctor-patient confidentiality or confidentiality of legal communications.

>>>>

---
title: "Datasheet for 'A dataset'"
author: 
  - Yang Zhou
  - Yuean Wang
thanks: "Code and data are available at: LINK."
date: "`09 March 2024`"
date-format: "09 March 2024"
abstract: "The CES 2022 dataset, collected through an online survey by YouGov, encompasses 60,000 instances representing U.S. adult citizens' electoral behaviors, political opinions, and demographic characteristics. The instances are detailed and categorized by election experiences, contextual data, demographic information (e.g., gender, race, education), political affiliations, and opinions on various policy issues. The dataset employs a matched random sampling methodology, with its representativeness validated through a two-stage weighting process involving entropy balancing and iterative proportional fitting. Preprocessing included sample matching, weighting, and vote validation, ensuring data quality and representativenes in order to avoid representative bias."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description
    - The Cooperative Election Study (CES) aims to study how Americans perceive and hold their representatives accountable during elections. Besides, the study also interested in understanding their voting behavior and how their behavior be affected by political geography and social context. They study the group by capturing mass data across most of legislative constituencies. CES aims to fill the gap of understanding the American electoral process by analyzing congressional elections and national surveys.

@@

	- The CES 2022 dataset consists primarily of structured survey data collected from respondents about their political views, behaviors, and demographic information. Such data is generally not subject to legal privileges such as doctor-patient confidentiality or confidentiality of legal communications.
